---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## This dynamic report is tracking characteristics regarding short-form content, such as a platform, video length, hastags, and comapring these results to help draw conclusions. 

```{r}
library(tidyverse)
library(magick)

# Reading in the data
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQJP_Rgunaou1bjyafu7-9Ga5PfUKm4GD98vFb4mwSrujLq2P1M2R96T9Upe_gSXyu2krPwA8cYmwG7/pub?output=csv")
  
# Storing the renamed data with the rename function, under the name of latest_data.
latest_data <- rename(logged_data, 
                       timestamp = 1, 
                       platform = 2, 
                       video_length_secs = 3, 
                       hashtag = 4)


# Using the nchar function to collect the number of characters in each hashtag, which allows me to create a new numeric value. 
char_hashtag <- nchar(latest_data$hashtag)

# Creates a new variable which replaces responses with no hashtags with NA
new_hashtag <- replace(char_hashtag, char_hashtag == 0, NA)

# Splitting the data by platform, to allow for analysis of each platform separately
split_platform <- split(latest_data, latest_data$platform)

# The mean length in seconds of submissions from Youtube Shorts
mean_shorts_video_length <- mean(split_platform$`Youtube Shorts`$video_length_secs)

# The mean length in seconds of submissions from Instagram Reels
mean_reels_video_length <- mean(split_platform$`Instagram Reels`$video_length_secs)

# The mean length in seconds of submissions from TikTok
mean_tiktok_video_length <- mean(split_platform$`TikTok`$video_length_secs)

# The mean length in seconds of submissions from X Shorts
mean_x_video_length <- mean(split_platform$`X Shorts`$video_length_secs)

# The mean length in seconds of submissions from other platforms
mean_other_video_length <- mean(split_platform$`X Shorts`$video_length_secs)


```

## The plot below displays the platforms on which the responses used. 

``` {r}

ggplot(data = latest_data) + 
  geom_bar(aes(x = platform),
           fill = "#0000FF",) + 
  labs(title = "Platform which respondents watched short-form content on", 
       x = "Platform", 
       y = "Videos submitted")

```

### This report includes a total number of `r length(latest_data$platform)` data points. 

`r length(split_platform$'Instagram Reels'$platform)` of the data points are from Instagram Reels

`r length(split_platform$'Youtube Shorts'$platform)` are from Youtube Shorts, 

`r length(split_platform$'TikTok'$platform)` are from TikTok,

`r length(split_platform$'X Shorts'$platform)` are from X Shorts

`r length(split_platform$'Other'$platform)` are from other platforms


## One aspect I think is important to explore is the mean video length of the each of the platforms.

The mean video length for Instagram Reels is `r mean_reels_video_length `.

The mean video length for Youtube Shorts is `r mean_shorts_video_length `.

The mean video length for TikTok is `r mean_tiktok_video_length `.

The mean video length for X Shorts is `r mean_x_video_length `.

The mean video length for other platforms is `r mean_other_video_length `.



## The plot below displays the number of characters used in the first hashtag of the submitted.

  *Please note that the plot does not include responses with no hashtags*

```{r}

ggplot(data = latest_data) +
  geom_bar(aes(x = new_hashtag, fill = platform)) +
  labs(title = "Number of characters in first hashtag",
       subtitle = "Does not include responses with no hashtags", 
       x = "Number of characters in first hashtag", 
       y = "Videos submitted")


```

Out of all of the data collected, the shortest hashtag contained `r min(new_hashtag, na.rm = TRUE)` characters, and the longest contained `r max(char_hashtag)`

